Implicit yaddayadda

### 2011-09-20 papers/PLDI2012/implicitization.tex
typo

@@

The current working subset of paths is stored using a compact representation,
such as Binary Decision Diagrams.

@@

Since we do not work on the entire transition graph but on a subset of it, we
have to cunjunct the formula $f(p_i)$ with the actual set of working paths,
noted $P$, expressed as a boolean formula, where the boolean variables are the
\emph{reachability predicates} of the control points. We can easily construct
this formula from the binary decision diagram using dynamic programming, and
avoiding an exponentially sized formula. In other words, we force the SMT solver
to give us a path which is in $P$.

@@

We distinguish two phases in the analysis of a point $p_i \in P_R$:
\begin{enumerate}
\item We search for paths starting at point $p_i$, such that these paths are in
$P$, i.e are included in the working subgraph. Each time we find a path, we
update the abstract value of the destination point of the path. This is the
phase explained in \ref{subsec:ascending}.
\item  When the precedent phase terminates, there is no more paths in
$P$, starting at $p_i$, 
that make the abstract values of the successors grow (otherwise, the SMT
solver would not have answered ``\emph{unsat}''). However, there may
exist such paths in the entire multigraph, that are not in $P$. The second phase
computes these paths and adds them to $P'$.
\end{enumerate}

>>>>

We also assume that the program in expressed in SSA form, meaning that each
variable is only assigned once in the transition graph. This is not a
restriction, since there exist standard algorithm that transform a program into
an SSA form.

@@

The current working subset of paths is stored using a compact representation,
such as binary decision diagrams.

@@

Since we do not work on the entire transition graph but on a subset of it, we
have to cunjunct the formula $f(p_i)$ with the actual set of working paths,
noted $P$, expressed as a Boolean formula, where the Boolean variables are the
\emph{reachability predicates} of the control points. We can easily construct
this formula from the binary decision diagram using dynamic programming, and
avoiding an exponentially sized formula. In other words, we force the SMT solver
to give us a path which is in $P$.

@@

We distinguish two phases when analysing a point $p_i \in P_R$:
\begin{enumerate}
\item We search for paths starting at point $p_i$, such that these paths are in
$P$, i.e are included in the working subgraph. Each time we find a path, we
update the abstract value of the destination point of the path. This is the
phase explained in \ref{subsec:ascending}.
\item  When the precedent phase terminates, there is no more paths in
$P$, starting at $p_i$, 
that make the abstract values of the successors grow (otherwise, the SMT
solver would not have answered ``\emph{unsat}''). However, there may
exist such paths in the entire multigraph, that are not in $P$. The second phase
computes these paths and adds them to $P'$.
\end{enumerate}
